Inequality in socioemotional skills: a cross-cohort comparison

### 2020-02-01 codes/R/paper/seskills_jpube_rev.Rnw
add multiple factor options EFA

@@

>>>>

<<BCSEFA_ADD, dependson='BCSEFA'>>=
@

<<MCSEFA_ADD, dependson='MCSEFA'>>=
@

@@

\begin{landscape}
\begin{table}
\caption{Loadings from exploratory factor analysis with 1 or 3 factors -- 11-item scale}\label{tab:load_add}
\centering\setstretch{1.2}\footnotesize
<<EFALOADTAB_ADD, dependson='MCSEFA_ADD', results='asis'>>=
# combine results
library(kableExtra)
loadtab <- cbind(meantab$num, meantab$title, 
                 data.frame(cbind(
                   bcsfa1.m$loadings,
                   bcsfa1.f$loadings,
                   bcsfa3.f$loadings,
                   mcsfa1.m$loadings,
                   mcsfa1.f$loadings,
                   mcsfa3.f$loadings
                 ))
                 )
colnames(loadtab) <- c("item", "title", 
                       "bcs1m", "bcs1f", "bcs3f1", "bcs3f2", "bcs3f3",
                       "mcs1m", "mcs1f", "mcs3f1", "mcs3f2", "mcs3f3"
)

loadtab %>%
  mutate_at(vars(matches("cs")), round, 3) %>%
  mutate_at(
    vars(matches("cs")),
    function(x) cell_spec(x, "latex", bold = ifelse(abs(x) > .3, TRUE, FALSE))
    ) %>%
  kable("latex", escape = F, booktabs = T, linesep = "", align=c('c','l','c','c','c','c','c','c','c','c','c','c'),
        col.names = c("Item", "Title", 
                      "Males", "Females", "Females Fac. 1", "Females Fac. 2", "Females Fac. 3",
                      "Males", "Females", "Females Fac. 1", "Females Fac. 2", "Females Fac. 3"
                      )) %>%
  column_spec(3:12, width = "5em") %>%
  add_header_above(c(" " = 2,  
                     "BCS (1970) - 1 Fac." = 2, "BCS (1970) - 3 Fac." = 3, 
                     "MCS (2000/1) - 1 Fac." = 2, "MCS (2000/1) - 3 Fac." = 3))

@
\justify {\scriptsize \emph{Notes}: The table displays the factor loadings obtained from exploratory factor analysis (EFA) on our novel scale, separately by cohort. The EFA is performed decomposing the polychoric correlation matrix of the items and using weighted least squares, and the solution is rescaled using oblique factor rotation (\emph{oblimin}). We use the \textbf{\textsf{R}} package \texttt{psych}, version 1.8.4 \citep{Revelle2018}.
\par}
\end{table}
\end{landscape}
